Classless Java

### 2016-03-23 OOPSLA16/sections/Translation.tex
section 3,4 some work completed today

\paragraph{Type preservation:}
Note that we preferred to introduce self, client and heir coherence instead of referring to conventional
type preservation theorems~\cite{}. The reason is
to better model how our approach behaves in a object oriented software ecosystem with inheritance,
where only some units may be translated/expanded.
Note inheritance crucial influence in heir coherence, and how client coherence allows
for only some units to be translated/expanded.
\bruno{I don't
  understand the point of the last sentence? Rephrase?}
  \marco{ok I tried to rephase the next sentence, how is now?}
This means that developers and designers of Java libraries and frameworks
can start using IB (and our \mixin annotation) in the evolution of their products
and still retain backward compatibility with their clients.

>>>>

\paragraph{Type preservation:}
Note that we preferred to introduce self, client and heir coherence instead of referring to conventional
type preservation theorems~\cite{}. The reason is
to better model how our approach behaves in a object oriented software ecosystem with inheritance,
where only some units may be translated/expanded.
Note inheritance crucial influence in heir coherence, and 
our formulation of client coherence allows to discuss about intermediate
stages where only some code units are translated/expanded, while conventional 
type preservation refers only to the completely translated program.
This means that developers and designers of Java libraries and frameworks
can start using IB (and our \mixin annotation) in the evolution of their products
and still retain backward compatibility with their clients.
